Scattering Auditory Scenes for Classification: Supervised and Unsupervised Approaches

### 2016-06-28 paper/structureScene.tex
finish writing part IV. E

In turn, a late integration scheme relies on probabilistic estimates over short-term windows of length $T$, which are subsequently aggregated to produce a final decision
\begin{equation}
\hat{y} = \arg \max_{y} \rho\Big(\big\{ \mathbb{P}\left[y \,\vert\, \mathbf{S}\boldsymbol{x}(t,\gamma) \right] \big\}_{t} \Big),
\end{equation}
where $\rho$ is a reduction function, such as sum, product, or majority vote \cite{Kittler1998}.

The principal drawback of early integration is that it drastically reduces the number of training instances at the classifier stage, down to one per auditory scene -- if we don't account for data augmentation.
In the context of the DCASE 2013 dataset, this corresponds to merely $10$ training instances per class, and $100$ instances overall, hence a risk of overfitting.
On the contrary, a late integration scheme for $T=188\textrm{ ms}$ would yield $128$ instances per auditory scene, resulting in $12800$ instances overall.
However, many of these instances may be silent or lack any salient properties of the category they are assigned to, hence an increase in bias and a risk of underfitting.
In short, early and late integration methods lie at opposite ends of the bias-versus-variance statistical tradeoff. We refer to \cite{Joder2009} for a comprehensive review of this problematic in the context of musical instrument recognition.

\subsection{Standardization}

\begin{equation}
\widetilde{\mathbf{S}}\boldsymbol{X}(\gamma, n) =
\dfrac{ \mathbf{S}\boldsymbol{X}(\gamma, n) -
\mathbb{E}[ \mathbf{S}\boldsymbol{X}(\gamma)]}{\sigma( \mathbf{S}\boldsymbol{X}(\gamma))}
\end{equation}
where $\mathbb{E}[ \mathbf{S}\boldsymbol{X}(\gamma)] = \frac{1}{N} \sum_{n=1}^{N} \mathbf{S}\boldsymbol{X}(\gamma,n)$ is the expected value of $\mathbf{S}\boldsymbol{X}(\gamma,n)$ and
\begin{equation}
\sigma(\mathbf{S}\boldsymbol{X} (\gamma)) =
\sqrt{\frac{1}{N-1} \sum_{n=1}^{N}
\left( \mathbf{S}\boldsymbol{X}(\gamma,n) - \mathbb{E}[\mathbf{S}\boldsymbol{X}] \right)^2}
\end{equation}
 is the sample standard deviation.

@@

\section{Supervised approach: support vector machines}
Support vector machines are large-margin binary discriminators with tunable regularization of misclassified examples.
% The training set is linearly separable in feature space.

>>>>

Conversely, a late integration scheme relies on probabilistic estimates over short-term windows of length $T$, which are subsequently aggregated to produce a final decision
\begin{equation}
\hat{y} = \arg \max_{y} \rho\Big(\big\{ \mathbb{P}\left[y \,\vert\, \mathbf{S}\boldsymbol{x}(t,\gamma) \right] \big\}_{t} \Big),
\end{equation}
where $\hat{y}$ is the estimated class label and $\rho$ is a reduction function, such as sum, product, or majority vote \cite{Kittler1998}.

The principal drawback of early integration is that it drastically reduces the number of training instances at the classifier stage, down to one per auditory scene -- if we don't account for data augmentation.
In the context of the DCASE 2013 dataset, this corresponds to merely $10$ training instances per class, and $100$ instances overall, hence an increase in variance in statistical estimation and a risk of overfitting.
On the contrary, a late integration scheme for $T=188\textrm{ ms}$ would yield $128$ instances per auditory scene, resulting in $12800$ instances overall.
However, many of these instances may be silent or lack any salient properties of the category they are assigned to, hence an increase in bias and a risk of underfitting.
In short, early and late integration methods lie at opposite ends of the bias-versus-variance statistical tradeoff. We refer to \cite{Joder2009} for a comprehensive review of this problematic in the context of musical instrument recognition.

\subsection{Standardization}
Let $\mathbf{S}\boldsymbol{X}(\gamma,n)$ be a dataset, where the indices $\gamma$ and $n$ respectively denotes features and examples.
It is commonly acknowledged that support vector machines should be trained on scaled features with null mean and unit variance, so as to avoid mismatch in numeric ranges.
This operation may also help making the dataset linearly separable in feature space.
\vl{Check this claim in DCASE 2013 time scattering features.}
To standardize $\mathbf{S}\boldsymbol{X}(\gamma,n)$, we apply the affine transformation
\begin{equation}
\widetilde{\mathbf{S}}\boldsymbol{X}(\gamma, n) =
\dfrac{ \mathbf{S}\boldsymbol{X}(\gamma, n) -
\mathbb{E}[ \mathbf{S}\boldsymbol{X}](\gamma)}{\sigma[ \mathbf{S}\boldsymbol{X}](\gamma)}
\end{equation}
where $\mathbb{E}[ \mathbf{S}\boldsymbol{X}](\gamma) = \frac{1}{N} \sum_{n=1}^{N} \mathbf{S}\boldsymbol{X}(\gamma,n)$ is the expected value of $\mathbf{S}\boldsymbol{X}(\gamma,n)$ and
\begin{equation}
\sigma[\mathbf{S}\boldsymbol{X}] (\gamma) =
\sqrt{\frac{1}{N-1} \sum_{n=1}^{N}
\left( \mathbf{S}\boldsymbol{X}(\gamma,n) - \mathbb{E}[\mathbf{S}\boldsymbol{X}] \right)^2}
\end{equation}
 is the sample standard deviation.

 The vectors $\mathbb{E}[\mathbf{S}\boldsymbol{X}(\gamma)]$ and $\sigma[\mathbf{S}\boldsymbol{X}](\gamma)$ are estimated from the training set only, and the same affine transformation is subsequently applied to all samples in the training set and the test set.

@@

\section{Supervised approach: support vector machines}
Support vector machines are large-margin binary discriminators with tunable regularization of misclassified examples.
